Portable Multi- and Many-Core Performance for Finite-Difference/Element Codes; Application to the Free-Surface Component of NEMO (NEMOLite2D 1.0).

### 2017-09-18 docs/papers/nemolite2d_performance/referee_response.txt

Page 15, line 5 - we were referring to the L3 cache. This has been clarified.

Figure 5 - it is a reflection of the fact that Gnu is free while the Intel and
Cray compilers have performance of the generated code as a key part of their
respective business models.

Page 18, line 9 - the NEMOLite2D performance for the 32x32 domain is
significantly greater than for the other domains because it largely
fits within L2 cache. We have calculated that the working-set size for
the momentum kernel is 136*n^2. For 32x32 this gives ~136KB while for
64x64 this gives ~544KB. The former will fit within L2 cache while the
latter will spill to L3 cache. In addition, recall that we only parallelise
the outermost loop (Sec. 2.2.1) so, for the 32x32 domain, there are only
32 items to be shared amongst the threads. We have added a note to the
text regarding this.

Figure 11 - the size of the Momentum kernels meant that
their resource use limited the occupancy that could be achieved.
Therefore COLLAPSE might only help the performance of the other kernels and
they only account for some 30% of the run-time. In addition, the kernels
had been parallelised by enclosing them within a !$acc kernels region
which leaves the details to the compiler. It would seem that in this
case the decisions made by the compiler were good and COLLAPSE provided
little or no benefit. The text has been altered to cover both of these
points.

### 2017-09-18 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
nemolite2d-paper: address comment on small effect of COLLAPSE in OpenACC

The smallest domain ($64^2$) does not contain sufficient parallelism
to fully utilise the GPU and only the parallelisation of the Flather
kernels has much effect on performance. In fact, this is a significant
optimisation for all except the largest domain size where only changes
to the Momentum kernel yield sizeable gains. Collapsing the 2D loop
nests has a small but beneficial effect for the majority of problem
sizes. Gains here are limited by the fact that this optimisation was
only beneficial for the non-Momentum kernels and these only account
for some 30\% of the run-time.

>>>>

The smallest domain ($64^2$) does not contain sufficient parallelism
to fully utilise the GPU and only the parallelisation of the Flather
kernels has much effect on performance. In fact, this is a significant
optimisation for all except the largest domain size where only changes
to the Momentum kernel yield sizeable gains. Collapsing the 2D loop
nests has a small but beneficial effect for the majority of problem
sizes.  The gains here are small for two reasons; first, the automatic
CUDA kernel generation performed by the compiler (as instructed by the
\texttt{kernels} directive) is working well for this code and second,
this optimisation was only beneficial for the non-Momentum kernels and
these account for just 30\% of the run-time.
